---
title: "Homework 2"
author: "Rikeem Sholes"
date: "May 20, 2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

---

## Exercise 2 of baseR for Biologists

---

```{r}
path.root <- "C:/Users/rikee/OneDrive/Documents/baseR-V2020.2/baseR-V2020.2"
path.exercises <- paste(path.root, "/data/exercise_dat", sep = "")
path.examples <- paste(path.root, "/data/powerpoint_dat", sep = "")
path.gitfolder <- "C:/Users/rikee/code/R_class/Homework"
```

### Changing working directory and listing files

```{r}
setwd(path.exercises)
list.files()
```

### Changing to R Class git repo and listing files

```{r}
setwd(path.gitfolder)
list.files()
```

### Checking current working directory

```{r}
getwd() #returns my active working directory
```

```{r}
ls()
```

### Changing working directory back to root and saving pathnames there

```{r}
setwd(path.root)
save(path.root, path.gitfolder, path.examples, path.exercises, file = "data/baseR.pathnames.RData") 
#Verified that they were made
```

### Reloading pathnames after restart

```{r}
setwd("C:/Users/rikee/OneDrive/Documents/baseR-V2020.2/baseR-V2020.2/data")
load("baseR.pathnames.RData")
ls()
```

#Couldn't figure out MikTeX installation to get this to output as a pdf. Couldn't find "complete" version that the Rstudios prompt recommended and the "basic" version didn't work.

---

## Done