---
title: "Homework_6"
author: "Rikeem Sholes"
date: "May 28, 2020"
output: html_document
---

---

## Exercise 6 of baseR for Biologists

---

##Assigning a dataset path
```{r}
path.root <- "C:/Users/rikee/OneDrive/Documents/baseR-V2020.2/baseR-V2020.2"
path.dataset_path = paste(path.root, "/data/exercise_dat", sep = "")
path.examples = paste(path.root, "/data/powerpoint_dat", sep = "")
```

##Setting directory with data in it as working directory
```{r setup}
knitr::opts_knit$set(root.dir = path.dataset_path)
```

##Importing first clsx file, checking dimensions and checking header
```{r}
coyote1 = read_excel("coyotebehav.xlsx")
head(coyote1)
dim(coyote1)
```

##Importing csv file, checking dimensions and checking header
```{r}
zapus1 = read.csv("zapusmorph.csv", na.strings = ".") #Blank cells are denoted with periods. Added argument to fix that
head(zapus1)
dim(zapus1)
```

##Importing second clsx file, checking dimensions and checking header
```{r}
fish1 = read_excel("fish_recapture.xlsx", skip = 1) #Skipped first title header to fix table
head(fish1)
dim(fish1)
```

##Importing dbf file, checking dimensions and checking header
```{r}
tmax1 = read.dbf("tmax_all.dbf")
head(tmax1)
dim(tmax1)
#Had to manually download and install old foreign zip (foreign_0.8-76.zip) Newer version requires R version 4 at least. I'm running 3.6
```


```{r}
setwd(path.examples)
m1 = read.csv("m1.csv")
m2 = read.csv("m2.csv")
m3 = read.csv("m3.csv")
m4 = read.csv("m4.csv")
t1 = read.csv("t1.csv")
w1 = read.csv("w1.csv")
f1 = read.csv("f1.csv")
```

---


# Done

---