---
title: "Homework 7"
author: "Rikeem Sholes"
date: "June 12, 2020"
output: html_document
---

---

## Exercise 7 of baseR for Biologists

---

## Assigning a dataset path

```{r}
path.root <- "C:/Users/rikee/OneDrive/Documents/baseR-V2020.2/baseR-V2020.2"
path.dataset_path = paste(path.root, "/data/exercise_dat", sep = "")
```

## Setting working directory

```{r setup}
knitr::opts_knit$set(root.dir = path.dataset_path)
```

## Importing zapusmorph database

---
```{r}
zap1.b = read.csv("zapusmorph.csv", header = T, na.strings = ".")
is.numeric(zap1.b$ELEV)
```

## Importing Coyote behavior file and check variable names

```{r}
coy1.b = read.csv("coyotebehav.csv", header = T)
names(coy1.b)
```

## Check whether each variable is numeric/factor and show levels

```{r}
str(coy1.b)
```

## Coercing habitat

```{r}
#We will force the habitat data into a factor
coy1.b$habitat = as.factor(coy1.b$habitat)
#Check to ensure coersion occured
is.factor(coy1.b$habitat)
```

## Convert coyote date/time format

```{r}
library(chron) #Loads chron library
coy1.b$c.date = dates(as.character(coy1.b$date))
coy1.b$c.time = times(coy1.b$time)
coy1.b$date.time = chron(dates = coy1.b$c.date, times = coy1.b$c.time)
str(coy1.b)
```

## Determine number of julian days since 01Jan1991

```{r}
julian(2, 27, 1991, origin =c(1, 1, 1991))
```

## Determine the number of hours and tenths of minutes since start/end of observation period

```{r}
difftime(coy1.b[675, 8], coy1.b[1, 8], units = "hours")
difftime(coy1.b[675, 8], coy1.b[1, 8], units = "mins")
```

## Import fish capture data

```{r}
fish1.b = read.csv("fish_recapture.csv", header = T, skip = 1)
attach(fish1.b)
```

## Determine the days between tag and recapture of each fish

```{r}
fish1.b$c.tagdate = dates(as.character(tag.date))
fish1.b$c.recapdata = dates(as.character(recap.date))
fish1.b$days.tag2recap = fish1.b$c.recapdata - fish1.b$c.tagdate 
```

---

# Done

---